Progress Report on the ``Adult Database'' analysis

### 2009-11-11 report/paper.tex
added preliminary cluster analysis.

@@

>>>>

Another method to analyze the dataset is based on the generation of clusters. 
Clusters are sets of data in which objects in the same cluster are similar, and
objects in different clusters are dissimilar. The first attempt at clustering
used only three variables: age, education\_num and hours\_per\_week, the same
variables we saw that had a greater impact on the amount gained by the
individual. The data was normalized using the Z-Transformation method and the 
K-Means method was used to obtain the final clusters, with a k of 6. Figures 
\ref{fig:cluster_1_age_education} and \ref{fig:cluster_1_education_hpw} show
scatter plots of the variables, colored by clusters. One thing one is able to
note is that people with younger age belong to cluster \#2. In terms of
education, people with higher education belong to cluster \#0, while people with
lower education belong to cluster \#1. In terms of hours of work per week, 
distribution is rather similar, but cluster \#2 and \#3 have a greater amount of
lower and higher values, respectively. Figure \ref{fig:cluster_1_cluster_plus50}
shows how clusters relate to the class values. Although the distribution is 
balanced, clusters \#1 and \#2 have a greater amount of people gaining below 
50K. Notice, as stated before, that this were the cluster having people with
lower education and younger age, respective.

@@

\begin{figure}
\centering
\includegraphics[width=10cm]{cluster_1_age_education.png}
\caption{Scatter plot of age and education}
\label{fig:cluster_1_age_education}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=10cm]{cluster_1_education_hpw.png}
\caption{Scatter plot of education and hours of work per week}
\label{fig:cluster_1_education_hpw}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=10cm]{cluster_1_cluster_plus50.png}
\caption{Scatter plot of cluster and class values of amount gained}
\label{fig:cluster_1_cluster_plus50}
\end{figure}
